Price of Anarchy for Mean Field Games

### 2018-07-30 PoA.tex
updated the numerical results descriptions

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Since we consider $\xi \equiv 1$ and the result still holds, we see that $Var(\xi)>0$ is not a necessary assumption. Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}. For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$. When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$. Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction through the states or interaction through the controls, and is thus an unnecessary assumption. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is thus an unnecessary assumption. This agrees with the conclusion of Remark \ref{remark_6}. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.

>>>>

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Since we consider $\xi \equiv 1$ and the result still holds, we see that $Var(\xi)>0$ is not a necessary assumption. Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}. For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$. When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$. Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is thus an unnecessary assumption. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is thus an unnecessary assumption. This agrees with the conclusion of Remark \ref{remark_6}. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
